GlobalSearchRegression.jl: \\ Building bridges between Machine Learning and Econometrics in Fat-Data scenarios

### 2019-07-12 paper/paper.tex
Update paper.tex

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

% Additional packages used%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm,amsmath,xcolor,caption}
%\usepackage[noend]{algpseudocode}
\usepackage{hyperref}
\DeclareMathOperator{\sgn}{sign}
\DeclareCaptionFont{lightblue}{\color{black}}
\captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
%\renewcommand{\thealgorithm}{\arabic{algorithm}}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{header}

\maketitle

\begin{abstract}
The aim of this paper is twofold. The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}
While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s -and newer- high-dimensionality concerns:
\begin{enumerate}
    \item Exponential increase in required information and execution time;
    \item Overfitting risk ; 
    \item Less-informative euclidean distances; and
    \item Unfeasible estimators. 
\end{enumerate}

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{amsmath}
\setcounter{page}{1}

\begin{document}
\input{header}
\maketitle
\begin{abstract}

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

\end{abstract}

\section{Introduction}
While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s -and newer- high-dimensionality concerns:
\begin{enumerate}
    \item Exponential increase in required information and execution time ;
    \item Overfitting risk; 
    \item Less-informative euclidean distances; and
    \item Unfeasible estimators. 
\end{enumerate}
